Why is time-to-resistance in mixtures influenced differently by effectiveness and exposure ?

### 2016-10-17 inst/documents/effectiveness_exposure_difference.Rmd
adding examples & finessing case

Increasing the exposure to one insecticide in a mixture has liitle influence 
on the time-to-resistance of the other. In contrast increasing the effectiveness 
of one insecticide in a mixture increases the time-to-resistance of the other.

@@

@@

plot_fit_rs(df_base, column='f', title='base')

plot_fit_rs(df_ef, column='f', title='effectiveness')

plot_fit_rs(df_ex, column='f', title='exposure')

@@

@@

So yes, increasing effectiveness I1 results in a decrease in the difference between the relative fitness of S & R to I2 (from 0.066 to 0.045), this can explain the slower selection for resistance.

In contrast increasing exposure to I1 results in an increase in the difference between the relative fitness of S & R to I2 (from 0.066 to 0.073), this can explain the faster selection for resistance.

Be a bit careful, does my normalising do anything weird ? I might be able to run calc_fit_rs() on the non normalised versions.
not normalised
calc_fit_rs(df_base_,'f')
      allele    meanfit
R1        R1 0.721
S1        S1 0.669
R2        R2 0.721
S2        S2 0.669
R1-S1  R1-S1 0.052
#R2-S2  R2-S2 0.052

calc_fit_rs(df_ef_,'f')
      allele    meanfit
R1        R1 0.666
S1        S1 0.583
R2        R2 0.641
S2        S2 0.608
R1-S1  R1-S1 0.083
#R2-S2  R2-S2 0.033

calc_fit_rs(df_ex_,'f')
      allele    meanfit
R1        R1 0.633
S1        S1 0.531
R2        R2 0.608
S2        S2 0.556
R1-S1  R1-S1 0.102
#R2-S2  R2-S2 0.052

>>>>

Increasing the exposure to one insecticide in a mixture has little influence 
on the time-to-resistance of the other. In contrast, increasing the effectiveness 
of one insecticide in a mixture increases the time-to-resistance of the other.

@@

scaneario exploration :

1. base : all inputs set to 0.5
1. effectiveness : effectiveness set to 0.8
1. exposure : exposure set to 0.8

@@

# before normalisation
```{r, eval=TRUE, echo=FALSE, results='hide', fig.width=2}

plot_fit_rs(df_base_, column='f', title='base', ylim=c(0.4,0.8))

plot_fit_rs(df_ef_, column='f', title='effectiveness', ylim=c(0.4,0.8), yblank=TRUE)

plot_fit_rs(df_ex_, column='f', title='exposure', ylim=c(0.4,0.8), yblank=TRUE)

# normalised
```{r, eval=TRUE, echo=FALSE, results='hide', fig.width=2}

plot_fit_rs(df_base, column='f', title='base', ylim=c(0.5,1))

plot_fit_rs(df_ef, column='f', title='effectiveness', ylim=c(0.5,1), yblank=TRUE)

plot_fit_rs(df_ex, column='f', title='exposure', ylim=c(0.5,1), yblank=TRUE)

@@

To look at this I calculated the mean fitness of the R & S alleles for each insecticide across all genotypes. (and I repeated this both for normalised and non-normalised fitnesses). This was done by multiplying the fitness of each genotype by the number of each allele and then calculating a mean.

```{r, eval=TRUE, echo=FALSE, results='markup'}
#just to give the example of the calculation
calc_fit_rs(df_base,'f',round_places=2, verbose=TRUE)
```

The difference between the resistant and susceptible allele for each insecticide (e.g. R1-S1) was then calculated.

@@

So yes, increasing effectiveness I1 results in a decrease in the difference between the relative fitness of S & R to I2 (from 0.066 to 0.045). This could explain the slower selection for resistance.

In contrast increasing exposure to I1 results in an increase in the difference between the relative fitness of S & R to I2 (from 0.066 to 0.073). This could explain the faster selection for resistance.

Similar results are obtained without normalising the fitnesses first.

#not normalised
```{r, eval=TRUE, echo=FALSE}

calc_fit_rs(df_base_,'f')
#R2-S2  R2-S2 0.052

calc_fit_rs(df_ef_,'f')
#R2-S2  R2-S2 0.033

calc_fit_rs(df_ex_,'f')
#R2-S2  R2-S2 0.052
